### 2021-08-05 paper/paper.tex
plot relative performance of the TreeMEsh

        \addplot[blue, mark=*, dashed, forget plot] % FLUXO, flux differencing
          table [x index=0, y index=3]{../data/pids_euler_ranocha_relative.dat};
%         \addplot[orange, mark=square*, dashed, forget plot] % TreeMesh, flux differencing
%           table [x index=0, y index=1]{../data/pids_euler_ranocha_relative.dat};
        \addplot[red, mark=diamond*, dashed] % StructuredMesh, flux differencing
          table [x index=0, y index=2]{../data/pids_euler_ranocha_relative.dat};
          \addlegendentry{Flux differencing}
      \end{axis}
    \end{tikzpicture}
    \caption{Run time relative to FLUXO.}
  \end{subfigure}%
  \caption{Run time per right-hand side evaluation and degree of freedom for
           different DG discretizations of the 3D compressible Euler equations.}
  \label{fig:PID-Euler}
\end{figure}

@@

\todo{TODO: Plot of this comparison with the \lstinline{TreeMesh}?}

>>>>

        \addplot[blue, mark=*, dashed, forget plot] % FLUXO, flux differencing
          table [x index=0, y index=3]{../data/pids_euler_ranocha_relative.dat};
%         \addplot[orange, mark=square*, dashed, forget plot] % TreeMesh, flux differencing
%           table [x index=0, y index=1]{../data/pids_euler_ranocha_relative.dat};
        \addplot[red, mark=diamond*, dashed] % StructuredMesh, flux differencing
          table [x index=0, y index=2]{../data/pids_euler_ranocha_relative.dat};
          \addlegendentry{Flux differencing}
      \end{axis}
    \end{tikzpicture}
    \caption{Run time relative to FLUXO.}
  \end{subfigure}%
  \caption{Run time per right-hand side evaluation and degree of freedom for
           different DG discretizations of the 3D compressible Euler equations
           in FLUXO (Fortran) and \trixi (Julia).}
  \label{fig:PID-Euler}
\end{figure}

@@

\todo{TODO: Keep the plot of this comparison with the \lstinline{TreeMesh}?}

\begin{figure}
\centering
  \begin{subfigure}{\linewidth}
    \begin{tikzpicture}[
      font=\footnotesize
      ]
      \begin{axis}[
          xlabel={Polynomial degree},
          % ylabel={Time per RHS call and DOF (relative)},
          ylabel={Relative run time {[-]}},
          width=\textwidth,
          height=0.66\textwidth,
          legend columns=-1,
          legend pos=south west,
          ymin=0.0,
          ymax=1.1,
          ytick={0, 0.2, 0.4, 0.5, 0.6, 0.8, 1},
          grid=major,
        ]
        \addplot[orange, mark=*, solid] % TreeMesh, weak form
          table [x index=0, y index=1]{../data/pids_euler_weak_cartesian.dat};
          \addlegendentry{Weak form}

        \addplot[orange, mark=*, dashed] % TreeMesh, flux differencing
          table [x index=0, y index=1]{../data/pids_euler_ranocha_cartesian.dat};
          \addlegendentry{Flux differencing}
      \end{axis}
    \end{tikzpicture}
  \end{subfigure}%
  \caption{Run time per right-hand side evaluation and degree of freedom for
           different DG discretizations of the 3D compressible Euler equations
           in FLUXO (Fortran) and \trixi (Julia).}
  \label{fig:PID-TreeMesh}
\end{figure}
